% Bibliography

%\label{app:bibliography} % Reference the bibliography elsewhere with \autoref{app:bibliography}
%
%\manualmark
%\markboth{\spacedlowsmallcaps{\bibname}}{\spacedlowsmallcaps{\bibname}} 
%\refstepcounter{dummy}
%
%\addtocontents{toc}{\protect\vspace{\beforebibskip}} % Place the bibliography slightly below the rest of the document content in the table of contents
%\addcontentsline{toc}{chapter}{\tocEntry{\bibname}}
%
%\bibliographystyle{plainnat}
%
%\bibliography{Bibliography}

\begin{thebibliography}{99}

\bibitem{[1]}
D. D. Murphy and C. C. Murphy, "A Gram-Charlier series method for calculating general signal constellation error probabilities", \emph{IEEE Transactions on Communications}, Vol. 60, Number 2, p. 300 - 305, 2012.

\bibitem{[2]}
Y. Yin, J. P. Fonseka and I. Korn, "Sensitivity to timing errors in EGC and MRC techniques", \emph{IEEE Transactions on Communications}, Vol. 51, Issue 4, p. 530 - 534, 2003.

\bibitem{[3]}
M. K. Simon and M.-S. Alouini, "Simplified noisy reference loss evaluation for digital communication in the presence of slow fading and carrier phase error", \emph{IEEE Transactions on Vehicular Technology}, Vol. 50, Issue 2, p. 480 - 486, 2001.

\bibitem{[4]}
N. A. Najib and V. K. Prabhu, "Analysis of equal-gain diversity with partially coherent fading signals", \emph{IEEE Transactions on Vehicular Technology}, Vol. 49, Issue 3, p. 783 - 791, 2000.

\bibitem{[5]}
X Tang, M.-S. Alouini and A. Goldsmith, "Effect of channel estimation error on M-QAM BER performance in Rayleigh fading", \emph{IEEE 49th Vehicular Technology Conference}, Vol. 2, p. 1111 - 1115, 1999.

\bibitem{[6]}
M. O. Sunay and P. J. McLane, "Probability of error for diversity combining in DS CDMA systems with synchronization errors", \emph{European Transactions on Telecommunications}, Vol. 9, Issue 5, p. 449 - 463, 1998.

\bibitem{[7]}
M. K. Simon, "A simple evaluation of DPSK error probability performance in the presence of bit timing error", \emph{IEEE Transactions on Communications}, Vol. 42, Issue 234, p. 263 - 267, 1994.

\bibitem{[8]}
J. Proakis and M. Salehi, \emph{Digital Communications}, 5th ed., New York: McGraw-Hill, 2008.

\bibitem{[20]}
D. Graffox. (2009, Sep). \emph{IEEE Citation Reference} [Online]. Available: \texttt{http://www.ieee.org/documents/ieeecitationref.pdf}

\end{thebibliography}